The formal verification of the ctm approach to forcing \thanks{Supported by Secyt-UNC projects 33620180100855CB and 33620180100465CB, and Conicet.}

### 2022-09-30 Independence_CH/sample_proof.tex
Spell-check

There has been some progress on assistants where one writes statements
and proofs in natural language; recently P.~Koepke and his team
achieved magnificient results by using Isabelle/Naproche
\cite{10.1007/978-3-030-81097-9_2} to formalize proofs of several
results (particularly, the proof of König's Theorem). The input
language of Isabelle/Naproche is a \emph{controlled} natural language
that presents the result being formalized as a deduction in
first-order logic, where every assumption and the ``whole logical
scenario'' are explicitly given. From the input language,
Isabelle/Naproche builds ``proof tasks'' that are handled to automatic
theorem provers. As far as we can tell, Isabelle/Naproche is
promising but still unsuitable for a project of the magnitude of ours.

>>>>

There has been some progress on assistants where one writes statements
and proofs in natural language; recently P.~Koepke and his team
achieved magnificent results by using Isabelle/Naproche
\cite{10.1007/978-3-030-81097-9_2} to formalize proofs of several
results (particularly, the proof of König's Theorem). The input
language of Isabelle/Naproche is a \emph{controlled} natural language
that presents the result being formalized as a deduction in
first-order logic, where every assumption and the ``whole logical
scenario'' are explicitly given. From the input language,
Isabelle/Naproche builds ``proof tasks'' that are handled to automatic
theorem provers. As far as we can tell, Isabelle/Naproche is
promising but still unsuitable for a project of the magnitude of ours.
